%-------------------------
% Resume in Latex
% Author : Gautham M
% License : MIT
%------------------------
\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}
\begin{center}
\textbf{{\huge Gautham M}}
\end{center}
%----------HEADING-----------------
\begin{tabular*}
{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{Contact: }& \textbf{ Address:} \\
  {15CO118.gautham@nitk.edu.in} & {Raj Krupa Deepika Nagara}\\
   {gauthamm1997@gmail.com} & {Kulai Mangalore}\\
  Phone:91-8904211683 & {D.K. Karnataka 575019}\\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {National Institute of Technology Karnataka}{Surathkal,India}
      {BTech in Computer science and Engineering(6th Semester);  CGPA: 6.84}{Aug. 2015 -- July. 2019}
    \resumeSubheading
      {Kendriya Vidyalaya No.1 Panambur (CBSE)}{Mangalore, India}
      {class 12; 87.4\%}{July. 2015}
    \resumeSubheading
      {NMPT High School Panambur (KSSEB)}{Mangalore, India}
      {class 10; 97.12\%}{June. 2013}
  \resumeSubHeadingListEnd

%-----------Skills---------------------
\section{Key Skills}
    \resumeItemListStart
    \resumeItem{Programming}
    {C/C++, Java, Python.}
    \resumeItem{Web and App Development:}
    {HTML, CSS, JavaScript, PHP, nodeJs.}
    \resumeItem{Frameworks:}
    {Angular 5, Bootstrap, LARAVEL, SpringMVC.}
    \resumeItem{Databases:}
    {My SQL,NoSQL.}
    \resumeItem{Machine Learning Libraries:}
    {Jupyter, Scikit, Numpy, Pandas.}
    \resumeItem{Simulators:}
    {ns-3.}
    \resumeItem{Operating Systems}
    {Windows 10, Ubuntu 18.04(Linux)}
    \resumeItem{Other Utility}
    {GIT, Junit}
    \resumeItemListEnd
%-----------EXPERIENCE-----------------
\section{Internships}
  \resumeSubHeadingListStart

    \resumeSubheading
      {BNY Mellon Technology}{Chennai, India}
      {Software Development Intern}{May 2018 - July 2018}
     
      \resumeItemListStart
        \resumeItem {Data Analysis}
         {Analyzed and Structured Raw Data Pertaining to the clients. }
         \resumeItem {User Interface Building}
         {Creation of User Interfaces using Angular 5 to access the database. }
          \resumeItem {Api Development}
         {Back-end For the Project was built on MVC Architecture using Spring Boot.}
          \resumeItem {Validation}
         {The data entered input received from the users are validated for standards and discrepancy at both UI and API Level}
         \resumeItem {Testing}
         {The Developed Apis were Tested using Spring Test and Junit .}
      \resumeItemListEnd

    \resumeSubheading
      {Enheit Online Pvt.ltd}{Chennai, India}
      {Web Development Intern}{May 2017 - July 2017}
      \resumeItemListStart
        \resumeItem{Gallary Page}
          {An Image Gallery Page was built using Laravel Php Frameworks }
        \resumeItem{Color detection }
          {The uploaded image was processed to detect colors which could be used for searching.}
        \resumeItem{User Interface Modifications}
          {The website was modified so as to Increase the user Friendliness.}
        \resumeItem{Social Media Login}
          {login with Facebook and Google plus were implemented.}
        \resumeItem{Api for App Interaction}
          {Apis were developed to interact with Android Applications}
      \resumeItemListEnd

    \resumeSubheading
      {IT Section Finance Division (EDP) of New Mangalore Port Trust  }{Mangalore, India}
      {Trainee}{December 2016}
      \resumeItemListStart
        \resumeItem{Port Operation System}
          {Analyzed various modules and sub-modules of Port Operations Management and Information System, Port
          Operations and Port Control Systems, }
        \resumeItem{ERP}
        {Studied the functionality of Enterprise Resource Planning, Hospital Management Systems used in the industry}
        \resumeItem{Servers}
        {Analysed the methodologies used for Server load sharing  Firewall systems  and Data Backup.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{CARED in Linux Kernel}
      {Implementation of Cautiously Adaptive Random Early Detection Active Queue Management System Algorithm in Linux
Kernel.}
    \resumeSubItem{Image Pre-Processing for OCR}
      {Improving the efficiency of OCR with image pre processing techniques like contrast changes, Thresholding, angle Correction.}
     \resumeSubItem{Water Quality analysis}
      {Given the factors determining quality of water at given place genetic algorithms were used to predict the quality of water.}
    \resumeSubItem{User Friendly Ping application for ns-3}
      {a module proposed where it becomes easy to ping a node on ns-3 Network simulator.}
    \resumeSubItem{K-Means Image Segmentation on Massively GPU Architecture }
      {Implement Kmeans image segmentation algorithm on CUDA GPU Architecture and compare the performance with CPU.}
    \resumeSubItem{CRC-Assisted Error Correction In a trellis coded System with bit stuffing}
      {Implemented using c++ and tested using client server model.}
     \resumeSubItem{ChatBot}
      {Using Sequence to Sequence Artificial Neural Network on Tensor flow to implement Simple Chat Bot .}
     \resumeSubItem{OS-SYM}
      {implements various concepts of operating System and also
works as a tutor for people with no prior knowledge about the topic using python Tkinter Library.}
     \resumeSubItem{OS-BOOT}
     {A capstone project on development of a operating system running on bochs simulator the accepts command for copy, create and delete files.}
    \resumeSubItem{RSA-SYM}
     {A simple C++ code to show the working of RSA Encryption Algorithm.}
    \resumeSubItem{GYM-Management}
     {Centralized maintenance and performance tracking System for tracking gym users Data.}
    \resumeSubItem{C Compiler }
     {A Simple c compiler with limited functionality that generates Intermediate code from C code built with yacc and lex.}
    \resumeSubItem{Web Development }
     {Couple of websites were developed E-commerce for collage students, Stock buy and sell, Scraping websites using Angular,PHP,Bootstrap. }
    
  \resumeSubHeadingListEnd


%--------Areas of Interest------------
\section{Areas of Interest}
{Algorithms, Data structures, Machine Learning, Artificial Intelligence,Computer Networks, Data Mining, Web Development}
%--------Awards and other Activities------------
\section{Awards and other Activities}
\begin{itemize}
   \vspace{-1pt} \item Selected for NTSE scholarship in which one thousand students were selected by aptitude test in the year 2011.\vspace{-5pt}
  \vspace{-1pt}  \item School runner up in class 10 by securing 97.12 \% marks in the year 2013.\vspace{-5pt}
  \vspace{-1pt}  \item  Successfully completed Inspire internship conducted by Department of Science and Technology for motivating talented \vspace{-5pt}
youth to take up research careers in winter 2014.
  \vspace{-1pt}    \item Attended 3 days workshop on ethical hacking organized by ‘Engineer’ NITK. \vspace{-5pt}
  \vspace{-1pt}    \item Completed Google Applied CS with android workshop.\vspace{-5pt}
   \vspace{-1pt}   \item Attended five days GIAN Course on Software Defined Networks at NITK Surathkal.\vspace{-5pt}
\end{itemize}
%--------Personnel Information------------

\section{Personnel Information}
  \resumeItemListStart
    \resumeItem{Date Of Birth}
    {04 August 1997}
     \resumeItem{Sex}
    {Male}
         \resumeItem{Hobbies}
    {Competitive Coding, taking up MOOC’s, Swimming, Traveling.}
  \resumeItemListEnd
%--------Profiles------------
\section{Profiles}
  \resumeSubHeadingListStart
    \resumeSubItem{GitHub}
      {https://github.com/GauthamMaraswami}
    \resumeSubItem{Linkedin}
      {https://www.linkedin.com/in/gautham-maraswami}
        \resumeSubItem{WebPage}
      {https://gauthammaraswami.github.io/}
        \resumeSubHeadingListEnd
%-------------------------------------------
\end{document}
